Gozde and Liora Replication Code

### 2015-04-23 replication.Rmd
Latest code with Gozde's edits

---
title: "Gozde and Liora Replication Code"
author: "Gozde Guran and Liora Goldensher"
date: "3/6/2015"
output: html_document
---
test
# Replication Code for "Contextual Factors and the Extreme Right Vote in Europe, 1980-2002" by Kai Arzheimer American Journal of Political Science (2009)

@@

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
library(msm)
asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
variable <- asy # identifying "asy" as the variable of interest so that the remaining code can be reused in the next graph with a different variable of interest specified
slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model) # Estimated variances
se <- rep(NA, length(asy))

for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x17) + (x36) * j, estmean, var)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

@@

unemployment <- seq(from = -5.908098, to = 12.291902, by = .01) # vector with possible values for unemployment
variable <- unemployment
slopes <- model$coef$fixed[16] + model$coef$fixed[36] * variable # Estimated slopes based on estimated coefficients of unemployment (16) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model)
se <- rep(NA, length(variable))

for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, var)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

@@

# Figure 2 (Conditonal Effects of Salience and Variance)
![Figure 2](figures/fig2.png)
```{r}
# Graph 1
salience <- seq(from = -3.108026, to = 21.872906, by=.1) # vector with possible values for salience
variable <- salience
slopes <- model$coef$fixed[21] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model)
se <- rep(NA, length(variable))

for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, var)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
variable.data <- cbind(variable, slopes, upper, lower)

@@

variance <- seq(from = -21.71426, to = 174.34497, by=10) # vector with possible values for variance
variable <- variance
slopes <- model$coef$fixed[20] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
se <- rep(NA, length(variable))
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, var)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

@@

grid.arrange(graph_3, graph_4, ncol = 1)
# Better scaled versions - not combined
graph_3
graph_4
```

>>>>

---
---
title: "Gozde and Liora Replication Code"
author: "Gozde Guran and Liora Goldensher"
date: "3/6/2015"
output: html_document
---

# Replication Code for "Contextual Factors and the Extreme Right Vote in Europe, 1980-2002" by Kai Arzheimer American Journal of Political Science (2009)

@@

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
library(msm)
asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01)) # vector with possible values for asylumseekers

variable <- asy # identifying "asy" as the variable of interest so that the remaining code can be reused in the next graph with a different variable of interest specified
slopes <- model$coef$fixed["z_unemp"] + model$coef$fixed["z_asylumseeker:z_unemp"] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop using the deltamethod function which approximates standard errors of transformation of parameters based on the given estimates of the mean and covariance (~ bootstrapping).
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x17) + (x36) * j, estmean, estvar)
}

# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

@@

unemployment <- seq(from = min(data$z_unemp), to = max(data$z_unemp), by = .01) # vector with possible values for unemployment
variable <- unemployment # standardized label
slopes <- model$coef$fixed["z_asylumseeker"] + model$coef$fixed["z_asylumseeker:z_unemp"] * variable # Estimated slopes based on estimated coefficients of asylumseekers (16) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

@@

# Figure 2 (Conditonal Effects of Salience and Variance)
![Figure 2](figures/fig2.png)
```{r}
# Graph 1
salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
variable <- salience
slopes <- model$coef$fixed["var_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
variable.data <- cbind(variable, slopes, upper, lower)

@@

variance <- seq(from = min(data$var_c), to = max(data$var_c), by=10) # vector with possible values for variance
variable <- variance
slopes <- model$coef$fixed["salience_mean_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors

for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

@@

grid.arrange(graph_3, graph_4, ncol = 1)
# Better scaled versions - not combined
graph_3
graph_4
`
```

# Model 1: Adorno Thesis (Personality Traits and Value Orientations)

```{r}
model1 <- glm(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + partner + left_right_scale + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)

# Model 2: Parsons Thesis (Social Disintegration)
```{r}
model2 <- glm(ext_vote ~ eu_neg + z_dem_satis + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
```

# Model 3: Group Conflict Model (Various theories)

```{r}
model3 <- glm(ext_vote ~ dispro_elect + federalism + z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
